MaxEnt: What is it good for?

### 2015-07-02 ms.tex
The prior probabilities
Changed constraint (so it will be a row when hypothesis space is a 3x3 grid)

Throughout this paper, we will look at examples of MaxEnt updating from a prior
$q(x)$ to a posterior $p(x)$ in different situations where the available
information takes different forms. The prior distribution for all of the
examples is a discrete prior over nine possible values of $x$, and is shown
in Figure~\ref{fig:distribution}.

@@

\begin{eqnarray}
P(D) = 1
\end{eqnarray}
where $D$ is a proposition about the value of $x$. For example, consider
updating from the prior $q(x)$ shown in Figure~\ref{fig:distribution}, to
a posterior $p(x)$, using the testable information
\begin{eqnarray}
P(3 \leq x \leq 5) = 1.\label{eq:prob_one}
\end{eqnarray}
Clearly, the distribution $q(x)$ doesn't satisfy this constraint. According
to $q(x)$ the probability that $x$ is 3, 4, or 5 is 0.225, not 1.
Therefore, we
need to update to a new distribution $p(x)$ using MaxEnt. It may not be
immediately obvious, but Equation~\ref{eq:prob_one} can be viewed as
a constraint on an expected value:
\begin{eqnarray}
\left<
\mathds{1}\left(3 \leq x \leq 5\right)
\right>_p = 1.
\end{eqnarray}
where $\mathds{1}()$ is an indicator function which returns 1 where the
argument is true and 0 where it is false. This allows us to use the
result for expected value constraints, given in
Section~\ref{sec:expectations}.

>>>>

Throughout this paper, we will look at examples of MaxEnt updating from a prior
$q(x)$ to a posterior $p(x)$ in different situations where the available
information takes different forms. The prior distribution for all of the
examples is a discrete prior over nine possible values of $x$, and is shown
in Figure~\ref{fig:distribution}. The nine prior probabilities are:

\begin{eqnarray}
\boldsymbol{q} = \{0.059, 0.167, 0.117, 0.048, 0.076, 0.231, 0.030, 0.082, 0.191\}.
\end{eqnarray}

The reason for choosing a ``ragged'' distribution is to avoid making any
connection between MaxEnt and notions of smoothness or locality, since these
do not actually play a role.

@@

\begin{eqnarray}
P(D) = 1
\end{eqnarray}
where $D$ is a proposition about the value of $x$. For example, consider
updating from the prior $q(x)$ shown in Figure~\ref{fig:distribution}, to
a posterior $p(x)$, using the testable information
\begin{eqnarray}
P(7 \leq x \leq 9) = 1.\label{eq:prob_one}
\end{eqnarray}
Clearly, the distribution $q(x)$ doesn't satisfy this constraint. According
to $q(x)$ the probability that $x$ is 7, 8, or 9 is 0.303, not 1.
Therefore, we
need to update to a new distribution $p(x)$ using MaxEnt. It may not be
immediately obvious, but Equation~\ref{eq:prob_one} can be viewed as
a constraint on an expected value:
\begin{eqnarray}
\left<
\mathds{1}\left(7 \leq x \leq 9\right)
\right>_p = 1.
\end{eqnarray}
where $\mathds{1}()$ is an indicator function which returns 1 where the
argument is true and 0 where it is false. This allows us to use the
result for expected value constraints, given in
Section~\ref{sec:expectations}.
